A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-11-05 sections/abstract/main.tex
Remove table of contents and add abstract

\begin{abstract}
    The main focus of this research is the construction of a 3-player game theoretic model between two queueing systems and a service that distributes individuals to them. The resultant model will then be used to explore dynamics between all players.

    The first aspect of this work is the development of a queueing system with two consecutive waiting spaces. The strategic managerial behaviour corresponds to how individuals use these waiting spaces. Two modelling techniques were used: discrete event simulation and Markov chains. The state probabilities of the Markov chain system have been used to extract the performance measures of the queueing model (e.g. mean time in each waiting room, mean number of individuals in each room, etc.).

    A 3-player game theoretic model is proposed between the two queueing systems and the service that distributes individuals to them. In particular this can be seen as a 2-player normal-form game where the utilities are determined by a third player with its own strategies and objectives. A backwards induction technique is used to get the utilities of the normal-form game between the two queueing systems.

    This particular system can be applied in a healthcare scenario where it captures the emergent behaviour between, for example, the Emergency Medical Service (EMS) and the Emergency Department (ED). This will be used to investigate the impact of target measures on patient welfare.
\end{abstract}

>>>>

\begin{abstract}
The focus of this research is the construction of a 3-player game theoretic 
model between two queueing systems and a service that distributes individuals 
to them. 
The resultant model will then be used to explore dynamics between all players.
The first aspect of this work is the development of a queueing system with two
consecutive waiting spaces. 
The strategic managerial behaviour corresponds to how individuals use these 
waiting spaces. 
Two modelling techniques were used: discrete event simulation and Markov chains.
The state probabilities of the Markov chain system have been used to extract 
the performance measures of the queueing model (e.g. mean time in each waiting
room, mean number of individuals in each room, etc.).
A 3-player game theoretic model is proposed between the two queueing systems
and the service that distributes individuals to them.
In particular this can be seen as a 2-player normal-form game where the 
utilities are determined by a third player with its own strategies and 
objectives. 
A backwards induction technique is used to get the utilities of the normal-form
game between the two queueing systems.
This particular system can be applied in a healthcare scenario where it 
captures the emergent behaviour between, for example, the Emergency Medical 
Service (EMS) and the Emergency Department (ED). 
This will be used to investigate the impact of target measures on patient 
well-being.
\end{abstract}
